What is disputed on the web?

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
Minor abstract tweaks while doing the initial submission
Discard these changes

@@

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Dan Byler\\
       \affaddr{School of Information}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{daniel.byler@berkeley.edu}
\and
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
\alignauthor Barbara Rosario\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
}

@@

\resolved{too much emphasis on {\em how}... rewrite following paragraph}

@@

The web contains a vast number of pages written by a vast number of people. In many cases, these people disagree with each other, and the pages they write contain conflicting information. For users to extract reliable information from the web, it is useful for them to be able to determine when different sources disagree about a topic.

In this paper we describe a method for automatically acquiring a corpus of disputed claims from the web. We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and that there are others that are making the claim. We are also interested in {\it who} disputes a particular claim, since a user is likely to be more interested in being told that a claim is disputed by a large number of sources that they believe are credible, rather than a small number of sources that they do not trust.

We identify disputed claims by searching for lexical patterns such as ``the misconception that $S$'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim. In Figure~\ref{templates} we list some of the patterns we used. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to filter out those strings that appear to make a well-formed claim.

We believe that this corpus will be useful for many purposes. We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources. We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in Internet debate  (Section~\ref{using}).

We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}. It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010. This amounts to approximately 1.1 million strings that we believe are making disputed claims. We plan to expand our corpus as we crawl more of the web and improve our algorithms.

By looking at the claims in this corpus, we see trends in dispute on the web that correspond to the debates that were particularly topical at particular times (Section~\ref{analysis}).

@@

The problem of determining information credibility on the web is becoming increasingly important. In the past a user would typically obtain information from a relatively small set of sources such as books, TV channels, and radio stations. The user would have some idea of the reputation and biases of each of these sources, and publishing barriers and quality control would ensure that these sources only published information that met their standards. 
The web is very different. A user has access to a vast number of different sources, but knows little about the biases or reputation of most of them. Moreover, the Internet has little in the way of publishing barriers or quality control. If a user is to extract reliable information from the web, they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.

There are several ways that a user can determine whether to trust information that they find on a web page. The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page meets their aesthetic criteria for a reliable web page; or they can check whether the information is consistent with information available from other sources.

A user can check the reputation of a source using a service such as SourceWatch.org, which publishes manually curated information about the reputation and known biases of various sources. Trustpilot.com produce a Firefox extension that warns a user when they are looking at a web page hosted by a company that they believe is not trustworthy. Alternatively, a user can simply use a search engine such as Google to look for information about the source. While these tools can be very useful, trustworthy sources sometimes publish unreliable information, and untrusted sources sometimes contain useful information. For example, a reliable source may have been misled by an unreliable source they were using themselves; or a small unrated blog may publish information that useful, insightful, and accurate.

@@

The problem of detecting disputed claims is closely related to the well-studied problem of detecting contradictions. A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true. For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''. A contradicted claim is not necessarily a disputed claim. In this example the person who said that the moon was made of rock might not be aware that others think it is made of cheese. A {\it contradiction} is logical, while a {\it dispute} is social. In order for a claim to be disputed, the authors of the documents must be aware that there is a contradiction between their beliefs.

@@

Detecting contradictions has proven to be a hard problem~\cite{Giampiccolo2007}. Much of this difficulty comes from the fact that one typically needs deep semantic and contextual knowledge to determine whether two statements that look like they might contradict each other actually do. For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush. ``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England. ``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times.

We detect disputes rather than contradictions. Rather than looking for claims that contradict each other, we look for evidence that people believe that there is a contradiction and that this contradiction is important. One advantage of looking for disputes rather than contradictions is that this allows humans to do the hard work of identifying contradictions and deciding whether they are important. If a page says ``Falsely claimed that George Bush is married to Barbara Bush'' then that suggests that the contradiction with ``George Bush is married to Laura Bush'' is likely to be genuine. The corresponding disadvantage is that if one looks for disputes, one will only detect contradictions that humans have found and believe are important.

@@

Another closely related area is sentiment analysis/opinion mining~\cite{Hu2004,Pang2004}. Opinion mining tries to determine what an author's opinion is about certain objects or certain features of certain objects. A focal application has been the automatic summarization of product reviews, to produce an overview of the product features that are viewed favorably or negatively. Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects.

\resolved{All merged? : The methods we use are closely related to related work on information extraction which is the task of identifying and classifying specific semantic entities within documents (i.e. names of locations, people, organizations, temporal expressions etc.) We described such related work in the next Section.}

@@

\begin{figure}[tb]
\begin{center}
  \begin{tabular}{|llll|}
    \hline
    {\bf Frequency$^*$} & {\bf Pattern} & {\bf Pattern} & {\bf Classifier}\\ 
    {\bf on the web} &                   & {\bf Precision} & {\bf Accuracy}\\
    \hline
        \multicolumn{2}{|l}{\it Plausible to not believe it} & &\\
	    & & &\\
        495,000,000 & believe that & 48\%& 65\%\\
        101,000,000 & claim that & 46\%& 72\%\\
       \hline
       \multicolumn{2}{|l}{\it It is notable that others believe it} & &\\
           & & &\\

@@

We implemented a three-stage process to build our corpus of disputed claims, each described in the following Sections. We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}). We then search the Web for these patterns (Section~\ref{searchpattern}). Finally, we filter the resulting strings to give only those that resemble unambiguous disputed claims (Section~\ref{filterclaim}).

@@

This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events. TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
These methods differ on how {\bf finish here}
\x{add more related work here}
\todo{add more related work here}

@@

@@

Not all patterns have exactly the same meaning. We grouped our patterns into three loose group, based on manual inspection of the pages that use them (Figure~\ref{templates}):

@@

 \item {\bf Plausible to not believe it:} The author feels the need to say that someone believes it, implying that it it plausible that someone else might not believe it. This is only subtly different from the previous group. For example ``Fans believe that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''. It is useful to exclude the cases where the pattern is prefixed by ``I'', since such sentences rarely contain useful disputed claims. For example ``John thinks Elvis is dead'' implies much more skepticism than ``I think Elvis is dead''. 
 \end{itemize}

@@

\begin{figure}
 \begin{center}
  \begin{tabular}{|llll|}
\hline
accuracy      & {\bf \#}    &  {\bf \%}  & {\bf   cum} \\
      \hline
dead on & 16   &   32\%  &   32\% \\
+/-10 d & 9    &   18\%  &   50\% \\
+/-30 d & 12   &   24\%  &   74\% \\
+/-90 d & 3    &   6\%   &   80\% \\
+/-1 yr & 6    &   12\%  &   92\% \\ 
>1 yr   & 4    &   8\%   &   100\% \\ 
\hline
  \end{tabular}
 \end{center}

 \label{dateaccuracy}
 \caption{Accuracy of simple date detection}
\end{figure}

@@

It is useful to be able to update our corpus as new pages appear on the web, without having to repeatedly download the same pages. The Yahoo BOSS API does not offer the ability to request only recent pages, or to specify a particular date range. We instead simulate this behavior by including a literal date string in the queries we pass to Yahoo BOSS. For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts. This approach has false positives and false negatives. Some web pages include dates that are not the date the article was posted, some web pages do not include the date the article was posted, and many web pages include dates in a different format. We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first). Despite being very primitive, this method seems to work reasonably well. When we manually inspected 50 pages retrieved by our algorithm, we found that 92\% written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}).

Knowing the rough date when someone believed or disputed something allows us te produce fuzzy time trends Section~\ref{timetrends}. Moreover, it is important to know when people believed particular things, since things that were true in the past may not be true any more (e.g. Elvis was alive in the past, but isn't not).

@@

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=18cm]{images/2by5.pdf}
	\caption{Frequency of each of the top nouns individually}
	\label{multiplot_nouns}
	\end{center}
\end{figure*}

@@

Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we might want to filter some of them out. a chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might by ambiguous what entities it is referring to (case 3).

The {\it P} column in Figure~\ref{templates} shows the percentage of the strings that match each pattern that we estimate to be unambiguous falsifiable claims. We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and unambiguous.

@@

We built a statistical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim. This is a classical text classification task; here the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification). Naive Bayes classifiers\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of documents\cite{mccallum98comparison}). We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.

The {\it A} column in Figure~\ref{templates} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim. To provide a baseline for what these figures mean, consider that a random classifier would have 50\% accuracy, a classifier that always said ``yes'' would have accuracy equal to the pattern precision (e.g. 62\% for ``the myth that''), and a classifier that always said ``no'' would have accuracy equal to 100 minus, the pattern precision (e.g. 52\% for ``believe that'').

We can observe that the patterns in the ``something false'' group perform much better than the patterns in ``plausible to not believe it'' group, but the ``plausible to not believe it'' group has a lot more hits. For the best patterns our classifier has accuracy in the high seventies.

Manual inspection suggests that the classifier is fairly good at filtering out strings that are not claims (case 1) but does poorly at working out whether a claim is unambiguous. This is not surprising. We anticipate that a more sophisticated technique with real world knowledge would be needed in order to determine whether a claim was unambiguous.

@@

We save the surrounding text, page title, and URL for each of the disputed claims we see made on the web. At present we do not do anything with this data, but we anticipate that it could be useful for many purposes. For example it may be possible to resolve the meaning of ambiguous words or entities based on the words nearby (with have experimented with an algorithm similar to that used by Wikify~\cite{Mihalcea2007}). It is also useful to what person wrote the page, what organization hosted the page, who they link to, what meme-like phrases they make near to the claim, whether the page is written in an ``expert'' style, etc.

@@

Dispute Finder~\cite{Ennals2010} is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that appear in web pages. Future iterations of Dispute Finder and other such agents will be designed to work with other media such as television or radio, as well as augmented reality applications. We envision a device that provides real-time feedback to users regarding claims made in a conversation or presentation. Such a device would augment individuals' intuitive recognition of that a disputed claim is being made.

@@

A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the zeitgeist of disputes. As an increasing proportion of human knowledge is brought to the web, these tools will be increasingly important in sociological and historical research.

\section{Analyzing the Data}
\label{analysis}
\input{analysis.tex}

We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010. This gave us a total of 1.8 million text strings, of which 1.1 million were identified by our classifier as being unambiguous disputable claims. Of those 1.1 million text strings, most are repeating claims made elsewhere in the data set.

\subsection{Trends over time}
\label{timetrends}

Figure~\ref{multiplot_nouns} shows the frequency with which particular nouns were discussed in particular years. We obtained these figures by using a part-of-speech tagger to identify nouns in claims found on January 10th of every year from 2000 to 2010. Although the date we searched for was in January, the claims we found are often from other points in the year, due to the fuzzy nature of our date search mechanism (Figure~\ref{dateaccuracy}). We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns. All graphs are plotted on the same scale. The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made. It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even the nouns prove to be quite interesting.

We manually inspected our claims to determine what was going on that made particular nouns spike at particular times:

\begin{itemize}
 \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention. His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
 \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006} seems to have sparked extra controversy.
 \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
 \item {\bf Israel:} The Gaza conflict of 2007 caused a big spike.  
\end{itemize}

These graphs resemble those produced by MemeTracker~\cite{Backstrom2009}, which graphed when particular memes were discussed on the web. They tracked highly repeated phrases, rather than nouns used in disputed claims.

\begin{figure}[tbh]
 \begin{center}
  \begin{tabular}{|lll|}
    \hline
    {\bf Noun} & {\bf Word Cluster} & {\bf Freq} \\
    \hline
   {\bf children} & tiger woods abused & 218\\
                  & instead encourage daily & 178\\
    \hline
   {\bf god} & daily encourage parents & 150 \\
   \hline
   {\bf government} & health care & 1267 \\
                    & united states & 427 \\
		    & relation environmental matters & 155 \\
   \hline
   {\bf iraq} & weapons mass destruction & 373 \\
              & united states & 247 \\
	      & saddam hussein & 192 \\
	      & al qaeda & 149 \\
   \hline
   {\bf israel} & middle east & 251 \\
		& allowed upon population & 128 \\
                & united states & 107 \\
		& off map & 106 \\
   \hline
   {\bf law}    & lawbreaker rather broken & 133 \\
		& united states &\\
   \hline
    {\bf obama} & working best interests & 568\\
                & health care & 481\\
	        & united states & 327 \\
		& nobel prize & 270 \\
		& legitimately president & 207 \\
		& ford hood shooter hasan nidal advised & 190 \\
		& birth certificate & 180\\
   \hline
   {\bf president} & united states & 439 \\
                   & health care & 203 \\
		   & george w & 164 \\
		   & aircraft system jolting bombing & 159 \\
		   & peace prize & 125 \\
		   & white house & 125 \\
   \hline
      {\bf war} & united states & 340 \\
   \hline

   {\bf women} & stay home & 183 \\
               & save vaccine & 85 \\
   \hline
  \end{tabular}
 \end{center}
 \label{cluster-figure}
 \caption{Largest word clusters found for nouns}
\end{figure}

\subsection{Clusters}
\label{clusters}

For each noun, we analyzed the claims about that noun, and produced clusters that represent claims about that noun that seem to be particularly hotly disputed. Rather than clustering claims directly, we instead cluster together words that frequently co-occur. We used an agglomerative clustering algorithm, repeatedly merging the two clusters of words that had the most claims in common.

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. Most of these will make sense to people who have been following news in the united states. For example, we see that disputed claims about Obama often talk about his Nobel prize or his birth certificate, and that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized). Some of the word clusters are not particularly interesting - for example many claims talk about the united states, even when that is not an important part of what is disputed.

>>>>

%%% jma mods  10AM  1 Feb 2010

% remove 
\newcommand{\jma}[1]{{\color{purple} #1}}

@@

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Dan Byler\\
       \affaddr{School of Information}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{daniel.byler@berkeley.edu}
\and
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
\alignauthor Barbara Rosario\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       %\email{john.m.agosta@intel.com} 
        \jma{\email{barbara.rosario@intel.com}}
}

@@

\resolved{too much emphasis on {\em how}... rewrite following paragrapgh}

@@

%jma we need to motivate dispute finding with credibility here
The web contains a vast number of pages written by a vast number of people. In many cases, these people disagree with each other, and the pages they write contain conflicting information. For users to extract reliable information from the web, it is useful for them to be able to determine when different sources disagree about a topic. \jma{Web pages commonly include disputes on topics they contain. Identifying disputes points out occasions where the credibility of a page could be called into question.}

In this paper we describe a method for automatically acquiring a corpus of disputed claims from the web. 
\jma{ A claim is a statement of opinion or fact found in the text of a page.} We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and that there are others that are making the claim. 
%jma  To be precise, it could also be vice versa - to suggest the claim is true and others say its false
We are also interested in {\it who} disputes a particular claim, since a user is likely to be more interested in being told that a claim is disputed by a large number of sources that they believe are credible, rather than a small number of sources that they do not trust.

We identify disputed claims by searching for lexical patterns such as ``the misconception that $S$'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author %themselves 
\jma{herself} disputes this claim. In Figure~\ref{templates} we list some of the patterns we used. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to \jma{select only} % filter out 
 those strings that appear to make a well-formed claim.

We believe that this corpus 
\jma{of claims}
will be useful for many purposes. We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources. We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in internet debate  (Section~\ref{using}).

We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}. It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010. This amounts to approxmately 1.1 million strings that we believe are making disputed claims. We plan to expand our corpus as we crawl more of the web and improve our algorithms.

By looking at the claims in this corpus, we see trends in dispute on the web that correspond to the debates that were particulary topical at particular times (Section~\ref{analysis}).

@@

The problem of determining information credibility on the web is becoming increasingly important. In the past a user would typically obtain information from a relatively small set of sources such as books, TV channels, and radio stations. The user would have some idea of the reputation and biases of each of these sources, and publishing barriers and quality control would ensure that these sources only published information that met their standards. 
The web is very different. A user has access to a vast number of different sources, but knows little about the biases or reputation of most of them. Moreover, the internet has little in the way of publishing barriers or quality control. If a user is to extract reliable information from the web, they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.

There are several ways that a user can determine whether to trust information that they find on a web page. The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page meets their aesthetic criteria for a reliable web page; 
% jma: you really mean look at the visual style of the page to infer reliability?
or they can check whether the information is consistent with information available from other sources.

A user can check the reputation of a source using a service such as SourceWatch.org, which publishes manually curated information about the reputation and known biases of various sources. Trustpilot.com produce a Firefox extension that warns a user when they are looking at a web page hosted by a company that they believe is not trustworthy. Alternatively, a user can simply use a search engine such as Google to look for information about the source\jma{'s reputation}. While these tools can be very useful, trustworthy sources sometimes publish unreliable information, and untrusted sources sometimes contain useful information. For example, a reliable source may have been misled by an unreliable source they were using themselves; or a small unrated blog may publish information that useful, insightful, and accurate.

@@

The problem of detecting disputed claims is closely related to the well-studied problem of detecting contradictions. A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true. For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''. 
%A 
\jma{But a} contradicted claim is not necessarily a disputed claim. In this example the person who said that the moon was made of rock might not be aware that others think it is made of cheese. A {\it contradiction} is logical, while a {\it dispute} is social. In order for a claim to be disputed, the authors of the documents must be aware that there is a contradiction between their beliefs.

@@

Detecting contradictions has proven to be a hard problem~\cite{Giampiccolo2007}. Much of this difficulty comes from the fact that one typically needs deep semantic and contextual knowledge to determine whether two statements that look like they might contradict each other actually do. 
\jma{Two instances of the same phrase may have the same sense, but a different reference. Or two different phrases may refer to the same thing.}
For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush. ``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England. ``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times.

We detect disputes rather than contradictions. Rather than looking for claims that contradict each other, we look for %evidence that people
\jma{linguistic clues that writers} believe that there is a contradiction and that this contradiction is important. One advantage of looking for disputes rather than contradictions is that this allows humans to do the hard work of identifying contradictions and deciding whether they are important. 
% jma better to use an example that really is false
If a page says ``Falsely claimed that George Bush is married to Barbara Bush'' then that suggests that the contradiction with ``George Bush is married to Laura Bush'' is likely to be genuine. The corresponding disadvantage 
\jma{would be that if one looks for disputes, one would} 
%is that if one looks for disputes, one will 
only detect contradictions that humans have found and believe are important.

@@

Another closely related area is sentiment analysis/opinion mining~\cite{Hu2004,Pang2004}. Opinion mining tries to determine what an author's opinion is about certain objects or certain features of certain objects. A focal application has been the automatic summarisation of product reviews, to produce an overview of the product features that are viewed favorably or negatively. Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects.

\resolved{All merged? : The methods we use are closely related to related work on information extraction which is the task of identifing and classifing specific semantic entities within documents (i.e. names of locations, people, organizations, temporal expressions etc.) We described such related work in the next Section.}

@@

\begin{figure}[tb]
\begin{center}
  \begin{tabular}{|llll|}
    \hline
    {\bf Frequency$^*$} & {\bf Pattern} & {\bf Pattern} & {\bf Classifier}\\ 
    {\bf on the web} &                   & {\bf Precision} & {\bf Accuracy}\\
    \hline
        \multicolumn{2}{|l}{\it Plausible to not believe it} & &\\
	    & & &\\

        570,000,000 & think that & 28\%& 69\%\\
        495,000,000 & believe that & 48\%& 65\%\\
        145,000,000 & idea that & 42\% & 61\%\\
        101,000,000 & claim that & 46\%& 72\%\\
       \hline
       \multicolumn{2}{|l}{\it It is notable that others believe it} & &\\
           & & &\\

@@

We implemented a three-stage process to build our corpus of disputed claims, each described in the following Sections. We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}). We then search the Web for these patterns (Section~\ref{searchpattern})
\jma{to collect strings containing them followed by a clause that is likely to be a disputed claim}.

Finally, we filter the resulting strings to give only those that resemble unambiguous disputed claims (Section~\ref{filterclaim}).

@@

% \jma{Remove this paragraph?}
This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events. TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
These methods differ on how {\bf finish here}
\x{add more related work here}
\todo{add more related work here}

@@

\include{modals}

%%% move this paragraph to the end of the section.

@@

Not all patterns have exactly the same meaning. We grouped our patterns into three loose 
\jma{groups}, based on manual inspection of the pages that use them (Figure~\ref{templates}):

% jma thinks this could be simply described as three epistemic cases: 
% 1) I don't believe it
% 2) Someone else believes it (and I don't)
% 3) Some else doesn't believe it (and I do)

@@

 \item {\bf Plausible to not believe it:} The author feels the need to say that someone believes it, implying that it it plausible that someone else might not believe it. This is only subtly different from the previous group. For example ``Fans think that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''. It is useful to exclude the cases where the pattern is prefixed by ``I'', since such sentences rarely contain useful disputed claims. For example ``John thinks Elvis is dead'' implies much more skepticism than ``I think Elvis is dead''. 
 \end{itemize}

@@

@@

It is useful to be able to update our corpus as new pages appear on the web, without having to repeatedly download the same pages. The Yahoo BOSS API does not offer the ability to request only recent pages, or to specify a particular date range. We instead simulate this behaviour by including a literal date string in the queries we pass to Yahoo BOSS. For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts. This approach has false positives and false negatives. Some web pages include dates that are not the date the article was posted, some web pages do not include the date the article was posted, and many web pages include dates in a different format. We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).

Including the date in the search also provides us with a light-weight way to sample what people believed or disputed at particular points in time Section~\ref{timetrends}. Moreover, it is important to know when people believed particular things, since things that were true in the past may not be true any more (e.g. Elvis was alive in the past, but isn't not).

@@

@@

% jma make this an un-numbered list? 
Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we might want to filter some of them out. 
%a 
\jma{A} chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might 
\jma{otherwise be ambiguous about}
%by ambiguous 
what entities it is referring to (case 3).

The {\it P} column in Figure~\ref{templates} shows the
\jma{precision for different patterns as the}
 percentage of the strings that match each pattern that we estimate to be unambiguous falsifiable claims. We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and \jma{unambiguous}.

@@

We built a \jma{statistical} classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim. We used a simple Bayesian classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.

The {\it A} column in Figure~\ref{templates} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim. In each case, we trained the classifier on the data set for the other patterns in the same group and then tested its performance on the result for that pattern.

We can observe that the patterns in the ``something false'' group 
\jma{ have higher coverage and}
perform much better than the patterns in ``plausible to not believe it'' group, but the ``plausible to not believe it'' group has a lot more hits.

@@

\x{Importance of dates}
\x{Work meaning depending on surrounding text}
\x{We do not yet do anything useful with context, but we believe it is important and intend to use it}
\x{context can be surrounding text but also features of the web pages -- domain,  "authority," in-links, format; context is also the author: expert? social info on author...}

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=16cm]{images/2by5.pdf}
	\caption{Frequency of each of the top nouns individually}
	\label{multiplot_nouns}
	\end{center}
\end{figure*}

@@

Dispute Finder is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that appear in web pages. Future iterations of Dispute Finder and other such agents will be designed to work with other media such as television or radio, as well as augmented reality applications. We envision a device that provides real-time feedback to users regarding claims made in a conversation or presentation. Such a device would augment individuals' intuitive recognition of that a disputed claim is being made.

@@

A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the %zeitgeist 
\jma{social dynamics of of disputes on the web.}
As an increasing proportion of human knowledge is brought to the web, these tools will be increasingly important in sociological and historical research.

\section{Analysing the Data}
\label{analysis}
\input{analysis.tex}

\x{Cite MemeTracker~\cite{Backstrom2009}}

\todo{Lots of pretty graphs showing what our data is like.}

\subsection{Data Quality}

\x{Look at a random sample of the data and say how clean it is.}
\x{Evaluate the quality of the claims that we extracted.}
\x{Evaluate the quality of the clusters that we created.}
\x{Evaluate the quality of the different individual patterns - which ones have the highest quality claims.}
\x{say something about {\em duplicate} claims?}

\subsection{Trends over time}

\x{Named entity recognition}

\x{Look at what noun phrases were most disputed at particular years.}
\x{Look at what noun phrases were most disputed on particular days.}

\x{We remove exact-match strings from the same domain - to avoid republishing of same article.}
